---
title: "p8105_homework1_kw3041"
output: github_document
date: "2025-09-20"
---

Here, I will run a code to display the first 6 rows of the dataset in order to access the data. 

```{r}
library(moderndive)
library(ggplot2)
library(tidyverse)
data("early_january_weather")
head(early_january_weather)
```

## Short description of this data set! 

This data includes variables such as `temp`, which is measured in Fahrenheit, and `dewp`, which is a measure of dewpoint; `humid` for relative humidity; `wind_speed`, and a few more variables. 

## Checking the structure of early_january_weather tibble:

The early_january_weather dataset contains following number of rows:
```{r}
nrow(early_january_weather)
```

The early_january_weather dataset contains the following numner of columns:
```{r}
ncol(early_january_weather)
```

The mean temperature of this dataset is:
```{r}
mean(early_january_weather[["temp"]], na.rm = TRUE)
```



## Plot of the Weather

```{r}
weather_plot <- ggplot2::ggplot(
  early_january_weather,
  ggplot2::aes(x = time_hour, y = temp, color = humid)
) +
  ggplot2::geom_point(alpha = 0.5) + 
  ggplot2::labs(
    title = "Temperature over Time; Colored by Humidity",
    x = "Time (hour)",
    y = "Temperature (F)",
    color = "Humidity"
  ) + 
    ggplot2::theme_minimal()

weather_plot
```
```{r}
ggplot2::ggsave("scatterplot_weather12.png", plot = weather_plot, width = 7, height = 4)
```

## Problem 2. Here, first I will set a random numeric sample. 

```{r}
set.seed(123) 
numeric_vec = rnorm(10)
```

```{r}
logical_vec = numeric_vec > 0
```

```{r}
char_vec = letters[1:10]
```

```{r}
factor_vec = factor(sample(c("Low", "Medium", "High"), size = 10, replace = TRUE ))
```


```{r}
df = data.frame(
  numeric_var = numeric_vec,
  logical_var = logical_vec,
  char_var = char_vec,
  factor_var = factor_vec
)

df
```

Taking mean from each variable

#Numeric and logical mean

```{r}
mean(df[ , "numeric_var"])
mean(df[, "logical_var"])
```

```{r}
mean(df[ , "char_var"])
mean(df[ , "factor_var"])
```

Only numeric and logical variables can be avergaed directly, if we wanted to get the avergae of facotrs and characters we would first need to convert or assign them a numeric conversion.